### 2022-08-10 manuscript.tex
Merge pull request #269 from SORTEE-Github-Hackathon/removing-table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/603d35edf8325ad77fc38594ae2a81ef11346da3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/603d35edf8325ad77fc38594ae2a81ef11346da3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2830986199

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9396d27adfc38e9204618775d08f1a56f0f98bb3/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9396d27adfc38e9204618775d08f1a56f0f98bb3}{SORTEE-Github-Hackathon/manuscript@9396d27}
on July 27, 2022.

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0628}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1851}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1669}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2562}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
\caption{a comparison of techNologies commonly used for collaborating on research in Ecology and Evolutionary Biology. In the first column, we group platforms for collaboration into broad guilds. The second column lists the platform for collaboration. The remaining columns indicate whether the platform for collaboration includes certain features. \label{tbl:compare}}\tabularnewline
Vesion control
Active real-time colalboration
Free \$
Vesion control
Active real-time colalboration
Free \$
Multi-tool & GitHub & Yes & Yes & Yes & NA & Broadly limited free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~ZeNodo, OSF). & 100 MB per file, 500 MB per private repository (2 GB for paid accounts). 100 GB for public repositories. Larger files (up to 2 GB) can be attached to releases. & NA \\
Multi-tool & OSF & Yes & Yes & Yes & Yes & Yes & Yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & Yes \\
Long-term (public) data repositories & PANGAEA & Yes & Yes & Yes & NA & Yes & Yes & 10 GB free & NA \\
Long-term (public) data repositories & ZeNodo & after published & after published & NA & NA & Yes & Yes & 50 GB per dataset & Yes \\
Long-term (public) data repositories & Dryad & after published & after published & NA & NA & Some journals cover cost & Yes & 300 GB per publication & Can link to individual files (Not entire reopository); Not really integrated \\
Long-term (public) data repositories & Figshare & Yes & Yes & Yes & NA & Yes & Yes & 20 GB free, up to 5 TB & Yes \\
Temporary (personal) drive storage & Google Drive & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & Yes \\
Temporary (personal) drive storage & Box & limited & Yes & ? & ? & NA & NA & Unlimited total size for subscription & Yes \\
Temporary (personal) drive storage & DropBox & limited & Yes & Yes & Yes & Limited free version \& paid & NA & 2 GB free & Yes \\
Temporary (personal) drive storage & One Drive and the Office Suite & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 5 GB free, up to 1TB paid & Yes \\
Collaborative code/text editors & Overleaf (online latex editor) & Yes & Yes & Yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & Yes \\
Collaborative code/text editors & Jupyter Notebook & Yes & ? & Yes & with Colab & Yes & NA & via Binder: No hard limit, but suggests No files \textgreater100 MB, can also store on GitHub or Google Colab & Yes \\
Collaborative code/text editors & HackMD & Yes & Yes & Yes & Yes & Yes & NA & 3 documents free, private invitee limits & Yes \\

@@

\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\tabularnewline

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/603d35edf8325ad77fc38594ae2a81ef11346da3/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/603d35edf8325ad77fc38594ae2a81ef11346da3}{SORTEE-Github-Hackathon/manuscript@603d35e}
on August 10, 2022.

@@

@@

\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology. In the first column, we group platforms for collaboration into broad guilds. The second column lists the platform for collaboration. The remaining columns indicate whether the platform for collaboration includes certain features. \label{tbl:compare}}\tabularnewline
